---
title: "FYP Analysis"
output:
  html_document:
    df_print: paged
---
**TODOs**:

Discussion points:

- exclusion criteria? 
- consider paying more
- language requirement: fluent or native? 

Future analyses:

- regressions to go with the graphs
- linguistic analyses

```{r set-up, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)
library(rlang)
theme_set(theme_bw())

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

##Data import constants
#data_location="data/pilotA/"
data_location="data/pilotB"
#date_start=lubridate::ymd('2021-02-22')
date_start=lubridate::ymd('2021-03-08')

image_location="write-ups/images"
```


```{r}
d.games <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
    filter(createdAt >= date_start)

d.chat.raw <- read_csv(here(data_location, 'rounds.csv')) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>%
  select(-data.target, -ends_with('response'), -ends_with('_correct'), -ends_with('time')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv("pilotB_chat.csv")

d.round_results.raw <- read_csv(here(data_location,'rounds.csv')) %>%
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("correct", "_correct", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  mutate(tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE)) %>% 
  mutate(correct=as.logical(correct),
         time=as.numeric(time)/1000) %>% 
  filter(!is.na(correct)) %>% 
  filter(playerId!=speaker)

game_ids_exclude <- d.round_results.raw %>% group_by(gameId) %>% tally() %>% filter(n!=144)

d.round_results <-  d.round_results.raw %>% anti_join(game_ids_exclude)
```

# Pilot stuff

```{r demographics}
d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>% 
  left_join(d.games, by = c('gameId')) %>% 
  anti_join(game_ids_exclude) %>% 
    rename_with(~ gsub("data.", "", .x, fixed = TRUE))

```

```{r feedback}

d.exit.survey %>% select( language, fair, chatUseful, feedback, time) %>% knitr::kable()

```

In terms of language, I used the prolific pre-filter for fluent in English (but not English as native), not sure what we want

How long did games take? Nothing took more than like 160 seconds (out of 180 possible). This is how long each game took (add 6 minutes of feedback time, and however long for intro and exit)



```{r}
d.round_results %>% group_by(trialNum, gameId) %>% 
           mutate(time= time %|% 180) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId) %>% 
  summarize(total_time=sum(max_time)/60)

```
We should consider paying more. 

Of 20 people recruited, 6 games started, 4 finished. 

# Pretty pictures


```{r chat}
d.chat <- d.chat.raw %>%
  #filter(role == 'speaker') %>%
  filter(!is.na(target)) %>% 
  mutate(text = gsub("\\n", '', fixed = T, text),
         text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>%
  group_by(gameId, trialNum, repNum, tangram, playerId, role, countCorrect) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words) %>% as.numeric(),
            total_num_chars = sum(utt_length_chars) %>% as.numeric()) %>%
  anti_join(game_ids_exclude) %>% 
  full_join(d.round_results, c("gameId", "trialNum", "repNum", "playerId", "tangram", "countCorrect")) %>% 
  mutate(text = text %|% "",
         total_num_words= total_num_words %|% 0,
         total_num_chars= total_num_chars %|% 0,
         role = role %|% "listener")

```

Everything here has bootstrapped 95% CIs. Speakers say less over the course of rounds. Also some tangrams are harder than others. 

```{r}
ggplot(d.chat, aes(x=repNum, y=total_num_words, color=role))+
  facet_wrap(~tangram, nrow=2)+
  scale_color_brewer(palette="Dark2")+
     stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Number of words", x="Round number")+
  theme(legend.position="bottom")

ggsave(here(image_location, 'words.pdf'), width=8, height=4)
# ggplot(d.chat, aes(x=repNum, y=total_num_chars, color=role))+
#   facet_wrap(~tangram)+
#     scale_color_brewer(palette="Dark2")+
#       stat_summary(fun.data = "mean_cl_boot")+
#     labs(title="Number of characters", y="Number of characters", x="Round number")
# 
# ggsave(here(image_location, 'chars.pdf'))


```

```{r accuracy}
d.round_results %>% group_by(playerId,repNum, gameId) %>% 
  summarize(pct_corr=sum(correct)) %>% 
  ggplot(aes(x=repNum, y=pct_corr))+
  stat_summary(fun.data = "mean_cl_boot")+
  #scale_color_brewer(palette="Dark2")+
  scale_y_continuous(breaks=c(0,3,6,9,12), limits = c(0,12))+
  labs(x="Round Number", y="Number correctly selected", title= "Overall accuracy increases over repetitions")

ggsave(here(image_location, 'accuracy.pdf'), width=6, height=3)

```


```{r time}
d.round_results %>% group_by(playerId, repNum, gameId) %>% 
  filter(correct==T) %>% 
  #summarize(time=mean(time)) %>% 
  ggplot(aes(x=repNum, y=time))+
  geom_jitter(width=.2, height=0, alpha=1, color="lightgrey")+
      stat_summary(fun.data = "mean_cl_boot")+
  scale_y_continuous(limits = c(0,180))+
    scale_color_brewer(palette="Dark2")+
  labs(x="Round Number", y="Time to selection in seconds",
       title="People choose faster in later rounds")

ggsave(here(image_location, 'time.pdf'), width=6, height=3)

```

Don't have enough data (especially on mistakes) to see differential utterance length decreases by condition. 

```{r}

d.previous.round <- d.chat %>% 
  ungroup() %>% 
  select(gameId,tangram,repNum,playerId, role, countCorrectround=countCorrect, total_num_words_prev=total_num_words, total_num_chars_prev=total_num_chars) %>% 
  unique() %>% 
  mutate(repNum=repNum+1)

 d.previous.trial <- d.chat %>% 
  ungroup() %>% 
  select(gameId,trialNum,playerId, role, countCorrecttrial=countCorrect, total_num_words_prev_trial=total_num_words, total_num_chars_prev_trial=total_num_chars) %>% 
  unique() %>% 
mutate(trialNum=trialNum+1)

d.chat.lagged <- d.chat %>%
  select(gameId, trialNum, repNum, playerId, role, tangram, total_num_words, total_num_chars) %>% 
  left_join(d.previous.round) %>% 
  mutate(reduction_word=log(total_num_words)-log(total_num_words_prev),
         reduction_char=log(total_num_chars)-log(total_num_chars_prev)) %>% 
  left_join(d.previous.trial) %>% 
  mutate(reduction_word_trial=log(total_num_words)-log(total_num_words_prev_trial),
         reduction_char_trial=log(total_num_chars)-log(total_num_chars_prev_trial)) %>%
  filter(repNum>0) %>% 
  filter(role=="speaker") %>% 
  mutate(prev_correct_round=as.factor(countCorrectround),
         prev_correct_trial=as.factor(countCorrecttrial),
         prev_all_correct_round=ifelse(countCorrectround==2,T,F))

ggplot(d.chat.lagged, aes(x=repNum, y=reduction_word, color=prev_correct_round))+
    scale_color_brewer(palette="Dark2")+
      stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
    labs(title="Change in utterance length", y="Log change in words", x="Round number")

ggplot(d.chat.lagged, aes(x=repNum, y=reduction_char, color=prev_correct_round))+
    scale_color_brewer(palette="Dark2")+
      stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
    labs(title="Change in utterance length", y="Log change in  chars", x="Round number")

# ggplot(d.chat.lagged, aes(x=repNum, y=reduction_word))+
#     scale_color_brewer(palette="Dark2")+
#       stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
#     labs(title="Change in utterance length", y="Log change in words", x="Round number")
# 
# ggplot(d.chat.lagged, aes(x=repNum, y=reduction_char, color=prev_all_correct_round))+
#     scale_color_brewer(palette="Dark2")+
#       stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
#     labs(title="Change in utterance length", y="Log change in  chars", x="Round number")

# ggplot(d.chat.lagged, aes(x=repNum, y=reduction_word_trial, color=prev_correct_trial))+
#     scale_color_brewer(palette="Dark2")+
#       stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
#     labs(title="Change in utterance length next trial", y="Log change in words", x="Round number")
# 
# ggplot(d.chat.lagged, aes(x=repNum, y=reduction_char_trial, color=prev_correct_trial))+
#     scale_color_brewer(palette="Dark2")+
#       stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
#     labs(title="Change in utterance length next trial", y="Log change in  chars", x="Round number")

```
