---
title: "FYP Analysis"
output:
  html_document: 
    toc: true
---



```{r set-up, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)
library(rlang)
library(lme4)
library(brms)
library(rstan)
library(viridis)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

##Data import constants
data_location="data/study1"


date_start=lubridate::ymd('2021-05-04')

image_location="write-ups/images"

model_location="code/models"

data_location_a <- "data/study1a"
data_location_b <- "data/study1b"

```

```{r}
##This was for determining participant bonuses using the version of data with PID
# d.treatments <- read_csv(here(data_location, 'treatments.csv')) %>% rename(treatmentId=`_id`)
# 
# d.games <- read_csv(here(data_location, 'games.csv')) %>%
#   select(gameId=`_id`, treatmentId, playerIds) %>%
#   left_join(d.treatments) %>%
#   mutate(playerIds=str_split(playerIds,",")) %>%
#   unnest(playerIds) %>%
#   select(playerId=playerIds, name)
# 
# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   left_join(d.games) %>%
#   select(data.bonus, playerId,id,data.bonus,name) %>%
#     filter(!is.na(name)) %>%
#   mutate(pc_bonus=case_when(
#     name=="fourRotate" ~ 3,
#     name=="threeRotate" ~ 1.5,
#     T ~ 0
#   )) %>%
#   mutate(bonus=round(data.bonus+pc_bonus,2),
#          cost=round(bonus*4/3,2)) %>% write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>% write_csv(here(data_location,"for_prolific.csv"))

# player_game <- read_csv(here("data/study1b/player-rounds.csv")) %>% select(playerId,gameId) %>% unique()
# player_id <- read_csv(here("data/players.csv")) %>% select(playerId=`_id`,id)
# summary %>% filter(numPlayers %in% c(5,6)) %>% filter(num_rounds==5) %>% left_join(player_game) %>% left_join(player_id) %>% mutate(bonus=2.7) %>% select(id,bonus) %>% write_csv(here("data/for_bonus.csv"))
```


```{r, include=F, eval=F}

d.games <- read_csv(here(data_location_a, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
    filter(createdAt >= date_start)

d.chat.raw <- read_csv(here(data_location_a, 'rounds.csv'), guess_max=10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>%
  select(-data.target, -ends_with('response'), -ends_with('_correct'), -ends_with('time')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv(here(data_location_a, 'raw_chat.csv'))

d.round_results.raw <- read_csv(here(data_location_a,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("correct", "_correct", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  mutate(tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE)) %>% 
  mutate(correct=as.logical(correct),
         time=as.numeric(time)/1000) %>% 
  filter(!is.na(correct)) %>% 
  filter(playerId!=speaker) %>% 
  write_csv(here(data_location_a, 'raw_results.csv'))

d.exit.survey <- read_csv(here(data_location_a, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv(here(data_location_a,'exit.csv'))



```


```{r, include=F, eval=F}

d.games <- read_csv(here(data_location_b, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
    filter(createdAt >= date_start)

d.chat.raw <- read_csv(here(data_location_b, 'rounds.csv'), guess_max=10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>%
  select(-data.target, -ends_with('response'), -ends_with('_correct'), -ends_with('time')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv(here(data_location_b, 'raw_chat.csv'))

d.round_results.raw <- read_csv(here(data_location_b,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("correct", "_correct", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  mutate(tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE)) %>% 
  mutate(correct=as.logical(correct),
         time=as.numeric(time)/1000) %>% 
  filter(!is.na(correct)) %>% 
  filter(playerId!=speaker) %>% 
  write_csv(here(data_location_b, 'raw_results.csv'))

d.exit.survey <- read_csv(here(data_location_b, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
    write_csv(here(data_location_b,'exit.csv'))


```

```{r}
#we exclude rounds where no one talked (this is our criteria for "they weren't playing anymore")
# this is better than if no one submitted b/c maybe people fail to click on some round?
rounds_include <- read_csv(here(data_location_a,'raw_chat.csv')) %>% union(read_csv(here(data_location_b,'raw_chat.csv'))) %>% 
  filter(!is.na(text)) %>%
  select(gameId,numPlayers,repNum,targetNum) %>% unique() %>% 
  group_by(gameId,numPlayers,repNum) %>% tally() %>% 
  filter(n==12) %>% select(gameId,repNum) %>% write_rds(here(data_location,"rounds_include.rds"))

d.round_results <-  read_csv(here(data_location_a,'raw_results.csv')) %>% union(read_csv(here(data_location_b,'raw_results.csv'))) %>% inner_join(rounds_include) %>% write_rds(here(data_location,'round_results.rds'))

# b/c countCorrect was being bad
d.correct <- d.round_results %>% 
  group_by(`_id`,gameId,target,targetNum,repNum,trialNum,
           numPlayers,countCorrect,speaker,tangram) %>% 
  summarize(realCorrect=sum(ifelse(correct,1,0)))

d.round_results %>% left_join(d.correct) %>% write_rds(here(data_location,"round_results.rds"))

d.exit_survey <- read_csv(here(data_location_a,'exit.csv')) %>% mutate(age=as.character(age)) %>%  union(read_csv(here(data_location_b,'exit.csv'))) %>% 
  write_csv(here(data_location,"exit_survey.csv"))
  
```
How many games

```{r}
d.round_results %>% group_by(gameId, numPlayers) %>% 
  summarize(max_rep=max(repNum)) %>% 
  mutate(game_length=ifelse(max_rep==5,"complete","partial")) %>% 
  group_by(numPlayers, game_length) %>% 
  tally() %>% 
  pivot_wider(names_from="game_length",values_from="n")
```

How long full games took

```{r}
summary <- d.round_results %>% group_by(trialNum, repNum, gameId, numPlayers) %>% 
           mutate(time= time %|% 180) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId, numPlayers) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum)) %>% 
  arrange(numPlayers)

message("Full games")

summary %>% filter(num_rounds==5) %>% 
  group_by(numPlayers) %>% 
  summarize(games=n(),
            min_time=min(total_time) %>% round(),
            `25th_time`=quantile(total_time, .25)%>% round(),
            median_time=quantile(total_time, .5)%>% round(),
            `75th_time`=quantile(total_time, .75)%>% round(),
            max_time=max(total_time)%>% round()) 

```


It shouldn't be possible to have times > 180 b/c the timer is 3 min

```{r}
d.round_results %>% filter(time>180) %>% group_by(gameId,playerId,numPlayers) %>% tally()
```

Not sure what is going on -- whether the timer was faulty in reality (took > 180) or whether the time recording was off. 




# Pretty pictures


```{r chat}

rounds_include <- read_rds(here(data_location,"rounds_include.rds"))
d.round_results <- read_rds(here(data_location,"round_results.rds"))
d.chat.filter <- read_csv(here(data_location, "filtered_chat.csv")) %>% 
  filter(!is.chitchat) %>% 
  filter(!is.na(target)) %>% 
  mutate(text = gsub("\\n", '', fixed = T, spellchecked), # note that this is using spellcorrected version!!!!
         text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>%
  group_by(gameId, trialNum, repNum, tangram) %>% 
  mutate(is.firstutter=ifelse(role!="speaker",F,NA)) %>% 
  fill(c("is.firstutter"), .direction="down") %>% 
  mutate(is.firstutter= is.firstutter %|% T) 

d.chat <- d.chat.filter %>% 
  group_by(gameId, trialNum, repNum, tangram, playerId, role, numPlayers) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words, na.rm=T) %>% as.numeric(),
            total_num_chars = sum(utt_length_chars, na.rm=T) %>% as.numeric()) %>%
  inner_join(rounds_include) %>% 
  full_join(d.round_results, c("gameId", "trialNum", "repNum", "playerId", "tangram", "numPlayers")) %>% 
  mutate(text = text %|% "",
         total_num_words= total_num_words %|% 0,
         total_num_chars= total_num_chars %|% 0,
         role = role %|% "listener")

d.chat.pre <- d.chat.filter %>% group_by(gameId, trialNum, repNum, tangram, playerId, is.firstutter,role, numPlayers) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words, na.rm=T) %>% as.numeric(),
            total_num_chars = sum(utt_length_chars, na.rm=T) %>% as.numeric()) %>%
  inner_join(rounds_include) %>% 
  ungroup() %>% 
  mutate(text = text %|% "",
         total_num_words= total_num_words %|% 0,
         total_num_chars= total_num_chars %|% 0,
         role = role %|% "listener") %>% 
  filter(is.firstutter)

```

Everything here has bootstrapped 95% CIs. 

Should find better curves to fit, but using quadratic to allow for some curvature.

```{r}
# ggplot(d.chat, aes(x=repNum, y=total_num_words, color=role))+
#   facet_wrap(~tangram, nrow=2)+
#   scale_color_brewer(palette="Dark2")+
#      stat_summary(fun.data = "mean_cl_boot")+
#   labs(title="Number of words", y="Number of words", x="Round number")+
#   theme(legend.position="bottom")

ggplot(d.chat, aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~role, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_jitter(alpha=.05)+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
     stat_summary(fun.data = "mean_cl_boot")+
    scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")

#ggsave(here(image_location, 'words.pdf'), width=6, height=4)

ggplot(d.chat, aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~role, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
     stat_summary(fun.data = "mean_cl_boot")+
  labs(title="Number of words", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")
```

```{r for-hai}
speaker_only <- d.chat %>% filter(role=="speaker")

s_count <- speaker_only %>% ungroup() %>% select(playerId) %>% unique()

p_count <- d.round_results %>% select(playerId) %>% unique()
ggplot(speaker_only, aes(x=repNum+1, y=total_num_words, color=as.factor(numPlayers), group=as.factor(numPlayers)))+
  scale_color_viridis(discrete=T, direction=-1)+
    geom_jitter(alpha=.05)+
    geom_smooth(method=glm, formula=y~poly(x,2), se=F, size=1.3)+
  #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
     stat_summary(fun.data = "mean_cl_boot", size=.5)+
    scale_y_continuous(limits = c(0,50))+
  scale_x_continuous(breaks=seq(1,6))+
  labs(y="Words from speaker", x="Round", color="Players")+
  theme(legend.position="right", axis.text=element_text(size=14), 
        axis.title=element_text(size=14),
        legend.text=element_text(size=14),
        legend.title=element_text(size=14))

ggsave(here(image_location, 'speaker_words.pdf'), width=5, height=3)
ggsave(here(image_location, 'speaker_words.png'), device="png", type="cairo",width=5, height=3)


d.round_results %>% group_by(playerId,repNum, gameId, numPlayers) %>% 
  mutate(correct.num=ifelse(correct,1,0)) %>% 
  ggplot(aes(x=repNum+1, y=correct.num, color=as.factor(numPlayers)))+
geom_smooth(method = "glm", method.args = list(family = "binomial"), size=1.3) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5)+
  scale_color_viridis(discrete=T, direction=-1)+
    scale_x_continuous(breaks=seq(1,6))+
  labs(x="Round", y="Selection Accuracy", color="Players")+
  theme(legend.position="right", axis.text=element_text(size=14), 
        axis.title=element_text(size=14),
        legend.text=element_text(size=14),
        legend.title=element_text(size=14))


ggsave(here(image_location, 'slide_accuracy.pdf'), width=5, height=3)
ggsave(here(image_location, 'square_accuracy.pdf'), width=5, height=5)

#ggsave(here(image_location, 'slide_accuracy.png'),device="png", type="cairo", width=5, height=3)

```
```{r}
square_acc <- d.round_results %>% group_by(playerId,repNum, gameId, numPlayers) %>% 
  mutate(correct.num=ifelse(correct,1,0)) %>% 
  ggplot(aes(x=repNum+1, y=correct.num, color=as.factor(numPlayers)))+
geom_smooth(method = "glm", method.args = list(family = "binomial"), size=1.3) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.3), size=.5)+
  scale_color_viridis(discrete=T, direction=-1)+
    scale_x_continuous(breaks=seq(1,6))+
  labs(x="Block", y="Selection Accuracy", color="Players")+
  theme(legend.position="none", axis.text=element_text(size=14), 
        axis.title=element_text(size=14),
        legend.text=element_text(size=14),
        legend.title=element_text(size=14))

save_plot(here(image_location,"square_accuracy.pdf"),square_acc, base_width=5, base_height=5)
```

```{r}
d.chat %>% filter(role=="speaker") %>% 
    mutate(groupxtangram=str_c(gameId,tangram)) %>% 
  group_by(repNum, numPlayers, gameId,tangram, groupxtangram) %>% 
  summarize(words=sum(total_num_words)) %>% 
ggplot(aes(x=repNum, y=words, color=as.factor(numPlayers)))+
  facet_wrap(~numPlayers, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_line(aes(group=groupxtangram), alpha=.1,method=glm, se=F)+
    #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  labs(title="Words from speaker per tangram", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="null")

#ggsave(here(image_location, 'words_lines.pdf'), width=6, height=4)

```

```{r}
d.chat %>% filter(role=="speaker") %>% 
ggplot(aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~tangram)+
  scale_color_brewer(palette="Dark2")+
    geom_smooth(method=glm, formula=y~poly(x,2), se=T, alpha=.1)+
    #  geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
       stat_summary(fun.data = "mean_cl_boot", size=.2)+
  labs(title="Tangram variability", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")

#ggsave(here(image_location, 'words_tangrams.pdf'), width=8, height=6)

```


Note: count correct has some issues so we should rederive this from the players.
(maybe something to do with multiple clients trying to update server at same time???)

```{r accuracy}
d.round_results %>% group_by(playerId,repNum, gameId, numPlayers) %>% 
  mutate(correct.num=ifelse(correct,1,0)) %>% 
  ggplot(aes(x=repNum, y=correct.num, color=as.factor(numPlayers)))+
geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
  #geom_point()+
  scale_color_brewer(palette="Dark2")+
  #scale_y_continuous(limits = c(0,1))+
  labs(x="Round Number", y="Fraction correctly selected", title= "Overall accuracy increases over repetitions", color="Player count")+
    theme(legend.position="bottom")


#ggsave(here(image_location, 'square_accuracy.pdf'), width=5, height=5)

```

```{r time}
d.round_results %>% group_by(playerId, repNum, gameId, numPlayers) %>% 
  filter(correct==T) %>% 
  #summarize(time=mean(time)) %>% 
  ggplot(aes(x=repNum, y=time, color=as.factor(numPlayers)))+
  geom_jitter(width=.4, height=0, alpha=.03)+
geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
  scale_y_continuous(limits = c(0,180))+
    scale_color_brewer(palette="Dark2")+
  labs(x="Round Number", y="Time to selection in seconds",
       title="People choose faster in later rounds", color="Player count")+
  theme(legend.position = "bottom")

#ggsave(here(image_location, 'time.pdf'), width=6, height=4)

```


# Models

```{r model-acc}
acc_input <- d.round_results %>% group_by(playerId,repNum, gameId, numPlayers) %>% 
  mutate(correct.num=ifelse(correct,1,0)) %>% 
  mutate(block=repNum,
         tangram_group=str_c(tangram, gameId))

priors <- c(set_prior("normal(0,1)", class="b"))#, #we're doing logistic, so these are reasonable b/c transform
                     # set_prior("normal(0,1)", class="sd"))

model <- brm(correct.num ~ block*numPlayers, 
             family=bernoulli(link="logit"),
             data=acc_input, 
             file=here(model_location, "acc_model"), prior=priors, control=list(adapt_delta=.95))
```

```{r model-time}
#note: there were some issues with time recording, source unknown. We exclude the obvious errors where time > 180, but it's probably still a bit dodgy?
time_input <- d.round_results %>% group_by(playerId, repNum, gameId, numPlayers) %>% 
  filter(correct==T) %>% 
  filter(time<181) %>% 
  filter(time>0) %>% 
  mutate(block=repNum,
         tangram_group=str_c(tangram, gameId))

priors <- c(set_prior("normal(0,100)", class="Intercept"),
            set_prior("normal(0,50)", class="b"))

model <- brm(time ~ block*numPlayers , 
             data=time_input, 
             file=here(model_location, "time_model"), prior=priors, control=list(adapt_delta=.95))

```

```{r model-listener, include=F}
listener_input <- d.chat %>% filter(role=="listener") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId))
         
priors <- c(
  set_prior("normal(0, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=listener_input,file=here(model_location, "listener_model"),                            prior=priors, control=list(adapt_delta=.95))

         

```

```{r model-speaker, include=F}
speaker_input <- d.chat %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=speaker_input,file=here(model_location, "speaker_model"),                            prior=priors, control=list(adapt_delta=.95))

         

```


```{r speaker-acc, include=F}
d.prev.speaker <- d.chat %>% ungroup() %>%  filter(role=="speaker") %>% select(gameId,repNum, tangram, total_num_words_prev=total_num_words)
d.prev.round <- d.chat %>% ungroup() %>% select(playerId, correct, tangram, gameId, repNum) %>% 
  left_join(d.prev.speaker) %>% unique() %>% mutate(repNum=repNum+1)


d.chat.lagged <- d.chat %>%
  ungroup() %>% 
  select(gameId, playerId, trialNum, repNum, playerId, role, tangram, total_num_words, numPlayers) %>%
  left_join(d.prev.round) %>%
  mutate(reduction_word=log(total_num_words)-log(total_num_words_prev)) %>%
  filter(repNum>0) %>%
  filter(role=="speaker") %>%
  mutate(prev_correct_round=correct)


model_input <- d.chat.lagged %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId),
         was_INcorrect=ifelse(!prev_correct_round,1,0))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_speaker_acc <- brm(words ~ block * numPlayers +block*was_INcorrect+ (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "speaker_acc"),                         prior=priors, control=list(adapt_delta=.95))

         
```


# Pre any listener commentary

```{r}
d.chat.pre %>% 
    mutate(groupxtangram=str_c(gameId,tangram)) %>% 
  group_by(repNum, numPlayers, gameId,tangram, groupxtangram) %>% 
  summarize(words=sum(total_num_words)) %>% 
ggplot(aes(x=repNum, y=words, color=as.factor(numPlayers)))+
  facet_wrap(~numPlayers, nrow=1)+
  scale_color_brew
er(palette="Dark2")+
    geom_line(aes(group=groupxtangram), alpha=.1,method=glm, se=F)+
    #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  labs(title="Words from speaker per tangram before a listener says anything", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="null")


```

```{r pre-backchannel, include=F}
model_input <- d.chat.pre %>%
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_no_backchannel <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "model_no_back"),                            prior=priors, control=list(adapt_delta=.95))

         

```



What's the model look like if we discard anything post listener talking? There's an effect of block, no effect on numPlayers, and some interaction. 

Hard to interpret since more people may jump in sooner. 

```{r}
summary(model_no_backchannel)
```

# First two rounds only
```{r first-rounds, include=F}
model_input <- d.chat %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId)) %>% 
  filter(block %in% c(0,1))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_first_2_rounds <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId), data=model_input,file=here(model_location, "model_2rounds"),                            prior=priors, control=list(adapt_delta=.95))

         

```

Speaker's experience at talking about these images is confounded with player count. However, this isn't true in the first two rounds, so we can limit to that. 
```{r}

summary(model_first_2_rounds)
```

# Pre-speaker repeats
Not sure if this is okay since unbalanced.

```{r , include=F}
model_input <- d.chat %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId)) %>% 
  filter(block < numPlayers)
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_test <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId), data=model_input,file=here(model_location, "model_pre_repeat"),                            prior=priors, control=list(adapt_delta=.95))

        

model_test2 <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "model_pre_repeat2"),                            prior=priors, control=list(adapt_delta=.95))

         

```

Speaker's experience at talking about these images is confounded with player count. However, this isn't true in the first two rounds, so we can limit to that. 
```{r}

summary(model_test)
```

# What if we code for speaker experience?
```{r , include=F}
model_input <- d.chat %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId)) %>% 
  mutate(speaker.repeat=ifelse(block<numPlayers,0,1))
  
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_test3 <- brm(words ~ block * numPlayers + block * speaker.repeat+(block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "model_code_repeat"),                            prior=priors, control=list(adapt_delta=.95))

        




```
