---
title: "FYP Analysis"
output:
  html_document:
    df_print: paged
---

# Data clean-up

```{r set-up, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)
theme_set(theme_bw())

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

##Data import constants
data_location="data/pilotA/"
date_start=lubridate::ymd('2021-02-22')
```


**Notes**: 

- numTrials etc were removed in code edits, so after another round of data will need to adjust code
- also check that trialnum is not messed up anymore
- and if time to selection is added, deal with that!!
- take out naming hacks

**TODOs**:
- need to filter out who's the speaker -- no one wants their responses! (or we could be hacky about it)

```{r}
d.games <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`)

d.chat.raw <- read_csv(here(data_location, 'rounds.csv')) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>%
  select(-data.target, -ends_with('response'), -ends_with('correct'),-data.numTrials,-data.reps,-data.numTargets, -data.roundbonus) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE))

d.round_results <- read_csv(here(data_location,'rounds.csv')) %>%
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("correct", "_correct", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  select(-numTrials, -reps, -numTargets, -chat,-roundbonus) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  mutate(speaker=case_when( ## THis is only here so I can get the rest of the pipeline relatively smoothly because what data recorded how was not optimal
    gameId=="mrpaHrMXHSntkA2Dy" ~"3cE5Tj2P4tigK262k",
    gameId=="WHTbegqrqojvuQoQi" ~ "DfGiwQJ7jqYfuGHoj",
    T ~ ""
  )) %>% 
  mutate(correct=as.logical(correct)) %>% 
  filter(!is.na(correct)) %>% 
  filter(playerId!=speaker)

```

Demographics are read in, but we don't care about them right now.

```{r demographics}
d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>% 
  left_join(d.games, by = c('gameId'))

```

Using some of Robert's code, could read roles off from game data, but I think it's easier to just keep track of who speaker is as a round-level variable, anyway?

```{r roles}

roles.tmp <- d.games %>%
  select(gameId, data.roleList) %>% 
  mutate(data.roleList = map(data.roleList, .f = ParseJSONColumn)) %>%
  unnest(data.roleList) %>%
  gather(playerId, role, -gameId) %>% 
  rowwise() %>% 
  filter(!is.null(role)) %>%
  unnest(role) %>%
  group_by(playerId) %>% 
  mutate(n = row_number() - 1,
         trialNum = n %% 12,
         roundNum = floor(n / 12)) %>%
  select(-n)
roles <- d.chat.raw %>%
  ungroup() %>%
  mutate(row_id = row_number()) %>%
  group_by(gameId, trialNum, repNum) %>%
  filter(row_id == first(row_id)) %>%
  summarize(playerId = unique(playerId)) %>%
  left_join(roles.tmp) %>%
  group_by(gameId, trialNum, repNum) %>%
  spread(role, playerId)
```

```{r chat}
d.chat <- d.chat.raw %>%
  #filter(role == 'speaker') %>%
  filter(!is.na(target)) %>% 
  mutate(text = gsub("\\n", '', fixed = T, text),
         text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>%
  group_by(gameId, trialNum, repNum, tangram, playerId, role) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words),
            total_num_chars = sum(utt_length_chars))
```

# Pretty pictures

```{r}
ggplot(d.chat, aes(x=repNum, y=total_num_words, color=playerId))+
  facet_wrap(~tangram)+
  geom_point()+
  geom_line()

ggplot(d.chat, aes(x=repNum, y=total_num_chars, color=playerId))+
  facet_wrap(~tangram)+
  geom_point()+
  geom_line()

```

```{r accuracy}
d.round_results %>% group_by(playerId,repNum) %>% 
  summarize(pct_corr=sum(correct)) %>% 
  ggplot(aes(x=repNum, y=pct_corr, color=playerId))+
           geom_line()+
  geom_point()+
  scale_y_continuous(breaks=c(0,3,6,9,12), limits = c(0,12))

```