---
title: "FYP Analysis"
output:
  html_document: default
  pdf_document: default
---



```{r set-up, include=F}
knitr::opts_chunk$set(echo = FALSE, warning=F, message=F)
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))
options(knitr.table.format = "html")
library(tidyverse)
library(jsonlite)
library(here)
library(rlang)
library(lme4)
library(brms)
library(rstan)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores())
theme_set(theme_bw())

ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T)
}

##Data import constants
data_location="data/study1"


date_start=lubridate::ymd('2021-05-04')

image_location="write-ups/images"

model_location="code/models"
```

```{r}
# This was for determining participant bonuses using the version of data with PID
# d.treatments <- read_csv(here(data_location, 'treatments.csv')) %>% rename(treatmentId=`_id`)
# 
# d.games <- read_csv(here(data_location, 'games.csv')) %>%
#   select(gameId=`_id`, treatmentId, playerIds) %>%
#   left_join(d.treatments) %>%
#   mutate(playerIds=str_split(playerIds,",")) %>%
#   unnest(playerIds) %>%
#   select(playerId=playerIds, name)
# 
# d.players <- read_csv(here(data_location, 'players.csv')) %>%
#   rename(playerId=`_id`) %>%
#   left_join(d.games) %>%
#   select(data.bonus, playerId,id,data.bonus,name) %>%
#     filter(!is.na(name)) %>%
#   mutate(pc_bonus=case_when(
#     name=="fourRotate" ~ 3,
#     name=="threeRotate" ~ 1.5,
#     T ~ 0
#   )) %>%
#   mutate(bonus=round(data.bonus+pc_bonus,2),
#          cost=round(bonus*4/3,2)) %>% write_csv(here(data_location, "player_payments.csv")) %>% select(id,bonus) %>% write_csv(here(data_location,"for_prolific.csv"))
```

# Pre-process

```{r, include=F, echo=F}
d.games <- read_csv(here(data_location, 'games.csv')) %>% 
  rename(gameId = `_id`) %>% 
    filter(createdAt >= date_start)

d.chat.raw <- read_csv(here(data_location, 'rounds.csv'), guess_max=10000) %>%
  filter(createdAt >= date_start) %>%
  mutate(data.chat = ifelse(is.na(data.chat), '{}', data.chat)) %>%
  rename(row_id = `_id`) %>%
  mutate(data.chat = map(data.chat, .f = ParseJSONColumn)) %>%
  unnest(data.chat) %>%
  select(-data.target, -ends_with('response'), -ends_with('_correct'), -ends_with('time')) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  write_csv(here(data_location, 'raw_chat.csv'))

d.round_results.raw <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  filter(createdAt >= date_start) %>% 
  rename_with(~ gsub("data.", "", .x, fixed = TRUE)) %>% 
  rename_with ( ~ gsub("room", "player", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("player", "player_", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("correct", "_correct", .x, fixed=T)) %>% 
    rename_with ( ~ gsub("response", "_response", .x, fixed=T)) %>% 
  rename_with( ~ gsub("time", "_time", .x, fixed=T)) %>% 
  select(-chat) %>% 
  gather(key, value, starts_with('player')) %>% 
  separate(key, into = c('blah', 'playerId', 'info')) %>% 
  spread(info, value) %>% 
  select(-blah) %>% 
  mutate(tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE)) %>% 
  mutate(correct=as.logical(correct),
         time=as.numeric(time)/1000) %>% 
  filter(!is.na(correct)) %>% 
  filter(playerId!=speaker)

#only include rounds that finished
rounds_exclude <- d.round_results.raw %>% group_by(gameId,numPlayers,repNum) %>% tally() %>% filter(n!=12*(numPlayers-1)) %>% select(gameId,repNum)

d.round_results <-  d.round_results.raw %>% anti_join(rounds_exclude) %>% write_rds(here(data_location,'round_results.rds'))

```


```{r} 
d.round_results <- read_rds(here(data_location,"round_results.rds"))
```


```{r, include=F, eval=F}
summary <- d.round_results %>% group_by(trialNum, repNum, gameId, numPlayers) %>% 
           mutate(time= time %|% 180) %>% 
  summarize(max_time=max(time)) %>% 
  group_by(gameId, numPlayers) %>% 
  summarize(total_time=sum(max_time)/60,
            num_rounds=max(repNum)) %>% 
  arrange(numPlayers)

#knitr::kable(summary)
message("Full games")
summary %>% filter(num_rounds==5) %>% group_by(numPlayers) %>% tally()
message("Partial games")
summary %>% filter(num_rounds!=5) %>% group_by(numPlayers) %>% tally()
```


# Demographics
```{r demographics}
d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE))

#d.exit.survey %>% select( language, fair, chatUseful, feedback, time) %>% knitr::kable()

```



# Pretty pictures


```{r chat}
d.chat.filter <- read_csv(here(data_location, "filtered_chat.csv")) %>% 
  filter(!is.chitchat) %>% 
  filter(!is.na(target)) %>% 
  mutate(text = gsub("\\n", '', fixed = T, text),
         text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         tangram = gsub('/experiment/tangram_', '', target, fixed=TRUE),
         tangram = gsub('.png', '', tangram, fixed=TRUE),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>%
  group_by(gameId, trialNum, repNum, tangram) %>% 
  mutate(is.firstutter=ifelse(role!="speaker",F,NA)) %>% 
  fill(c("is.firstutter"), .direction="down") %>% 
  mutate(is.firstutter= is.firstutter %|% T) 

d.chat <- d.chat.filter %>% 
  group_by(gameId, trialNum, repNum, tangram, playerId, role, countCorrect, numPlayers) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words) %>% as.numeric(),
            total_num_chars = sum(utt_length_chars) %>% as.numeric()) %>%
  anti_join(rounds_exclude) %>% 
  full_join(d.round_results, c("gameId", "trialNum", "repNum", "playerId", "tangram", "countCorrect", "numPlayers")) %>% 
  mutate(text = text %|% "",
         total_num_words= total_num_words %|% 0,
         total_num_chars= total_num_chars %|% 0,
         role = role %|% "listener")

d.chat.pre <- d.chat.filter %>% group_by(gameId, trialNum, repNum, tangram, playerId, is.firstutter,role, countCorrect, numPlayers) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words) %>% as.numeric(),
            total_num_chars = sum(utt_length_chars) %>% as.numeric()) %>%
  anti_join(rounds_exclude) %>% 
  ungroup() %>% 
  mutate(text = text %|% "",
         total_num_words= total_num_words %|% 0,
         total_num_chars= total_num_chars %|% 0,
         role = role %|% "listener") %>% 
  filter(is.firstutter)

```

Everything here has bootstrapped 95% CIs. 

Should find better curves to fit, but using quadratic to allow for some curvature.

```{r}
# ggplot(d.chat, aes(x=repNum, y=total_num_words, color=role))+
#   facet_wrap(~tangram, nrow=2)+
#   scale_color_brewer(palette="Dark2")+
#      stat_summary(fun.data = "mean_cl_boot")+
#   labs(title="Number of words", y="Number of words", x="Round number")+
#   theme(legend.position="bottom")

ggplot(d.chat, aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~role, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_jitter(alpha=.05)+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
     stat_summary(fun.data = "mean_cl_boot")+
    scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")

ggsave(here(image_location, 'words.pdf'), width=6, height=4)
```

```{r}
d.chat %>% filter(role=="speaker") %>% 
    mutate(groupxtangram=str_c(gameId,tangram)) %>% 
  group_by(repNum, numPlayers, gameId,tangram, groupxtangram) %>% 
  summarize(words=sum(total_num_words)) %>% 
ggplot(aes(x=repNum, y=words, color=as.factor(numPlayers)))+
  facet_wrap(~numPlayers, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_line(aes(group=groupxtangram), alpha=.1,method=glm, se=F)+
    geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
    #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  labs(title="Words from speaker per tangram", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="null")

ggsave(here(image_location, 'words_lines.pdf'), width=6, height=4)

```
Pre any listener commentary

```{r}
d.chat.pre %>% 
    mutate(groupxtangram=str_c(gameId,tangram)) %>% 
  group_by(repNum, numPlayers, gameId,tangram, groupxtangram) %>% 
  summarize(words=sum(total_num_words)) %>% 
ggplot(aes(x=repNum, y=words, color=as.factor(numPlayers)))+
  facet_wrap(~numPlayers, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_line(aes(group=groupxtangram), alpha=.1,method=glm, se=F)+
    geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
    #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  labs(title="Words from speaker per tangram before a listener says anything", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="null")


```

```{r}
d.chat %>% filter(role=="speaker") %>% 
ggplot(aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~tangram)+
  scale_color_brewer(palette="Dark2")+
    #geom_smooth(method=glm, formula=y~poly(x,2), se=T, alpha=.1)+
      geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
       stat_summary(fun.data = "mean_cl_boot", size=.2)+
  labs(title="Tangram variability", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")

ggsave(here(image_location, 'words_tangrams.pdf'), width=8, height=6)

```

```{r accuracy}
d.round_results %>% group_by(playerId,repNum, gameId, numPlayers) %>% 
  mutate(correct.num=ifelse(correct,1,0)) %>% 
  ggplot(aes(x=repNum, y=correct.num, color=as.factor(numPlayers)))+
geom_smooth(method = "glm", method.args = list(family = "binomial")) + 
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
  #geom_point()+
  scale_color_brewer(palette="Dark2")+
  #scale_y_continuous(limits = c(0,1))+
  labs(x="Round Number", y="Fraction correctly selected", title= "Overall accuracy increases over repetitions", color="Player count")+
    theme(legend.position="bottom")


ggsave(here(image_location, 'accuracy.pdf'), width=6, height=4)

```


```{r time}
d.round_results %>% group_by(playerId, repNum, gameId, numPlayers) %>% 
  filter(correct==T) %>% 
  #summarize(time=mean(time)) %>% 
  ggplot(aes(x=repNum, y=time, color=as.factor(numPlayers)))+
  geom_jitter(width=.4, height=0, alpha=.03)+
geom_smooth(method = "glm", formula = y~x,
                      method.args = list(family = gaussian(link = 'log')))+
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2))+
  scale_y_continuous(limits = c(0,180))+
    scale_color_brewer(palette="Dark2")+
  labs(x="Round Number", y="Time to selection in seconds",
       title="People choose faster in later rounds", color="Player count")+
  theme(legend.position = "bottom")

ggsave(here(image_location, 'time.pdf'), width=6, height=4)

```

```{r}
d.chat %>% filter(role=="speaker") %>% 
  mutate(all_correct=countCorrect==numPlayers-1) %>% 
    group_by(repNum, numPlayers, gameId, tangram, all_correct) %>% 
  summarize(words=sum(total_num_words)) %>% 
ggplot(aes(x=repNum, y=words, color=all_correct))+
  #facet_wrap(~all_correct)+
  scale_color_brewer(palette="Dark2")+
  geom_jitter(alpha=.05)+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  labs(title="Words from speaker per tangram", y="Number of words", x="Round number", color="Was everyone correct?")+
  theme(legend.position="bottom")


```
# Models

```{r, include=F}
model_input <- d.chat %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "model_acc"),                            prior=priors, control=list(adapt_delta=.95))

         

```

```{r, include=F}
d.prev.speaker <- d.chat %>% ungroup() %>%  filter(role=="speaker") %>% select(gameId,repNum, tangram, total_num_words_prev=total_num_words)
d.prev.round <- d.chat %>% ungroup() %>% select(playerId, correct, tangram, gameId, repNum) %>% 
  left_join(d.prev.speaker) %>% unique() %>% mutate(repNum=repNum+1)


d.chat.lagged <- d.chat %>%
  ungroup() %>% 
  select(gameId, playerId, trialNum, repNum, playerId, role, tangram, total_num_words, numPlayers) %>%
  left_join(d.prev.round) %>%
  mutate(reduction_word=log(total_num_words)-log(total_num_words_prev)) %>%
  filter(repNum>0) %>%
  filter(role=="speaker") %>%
  mutate(prev_correct_round=correct)


model_input <- d.chat.lagged %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId),
         was_INcorrect=ifelse(!prev_correct_round,1,0))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_speaker_acc <- brm(words ~ block * numPlayers +block*was_INcorrect+ (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "speaker_acc"),                         prior=priors, control=list(adapt_delta=.95))

         
```

```{r first-rounds, include=F}
model_input <- d.chat %>% filter(role=="speaker") %>% 
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId)) %>% 
  filter(block %in% c(0,1))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_first_2_rounds <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId), data=model_input,file=here(model_location, "model_2rounds"),                            prior=priors, control=list(adapt_delta=.95))

         

```

```{r pre-backchannel, include=F}
model_input <- d.chat.pre %>%
  mutate(block=repNum,
         words=total_num_words,
         tangram_group=str_c(tangram, gameId))
         
priors <- c(
  set_prior("normal(20, 20)", class="Intercept"),
  set_prior("normal(0, 10)", class="b"),
  set_prior("normal(0, 10)", class="sd"),
  set_prior("lkj(1)",       class="cor"))

model_no_backchannel <- brm(words ~ block * numPlayers + (block|tangram)+ (1|playerId)+(1|tangram_group)+(block|gameId), data=model_input,file=here(model_location, "model_no_back"),                            prior=priors, control=list(adapt_delta=.95))

         

```

Overall model predicting number of speaker words from block and player count. 

```{r}

summary(model)

```

Speaker's experience at talking about these images is confounded with player count. However, this isn't true in the first two rounds, so we can limit to that. 
```{r}

summary(model_first_2_rounds)
```

What's the model look like if we discard anything post listener talking? There's an effect of block, but not a large effect of number of players, no interaction. 

```{r}
summary(model_no_backchannel)
```

```{r}


summary(model_speaker_acc)

```
# Pre-process for NLP

```{r}

exchanges <- read_csv(here(data_location, "filtered_chat.csv")) %>% 
  filter(is.chitchat==F) %>% 
  select( -index, -stageIds, -is.chitchat, -submitted, -speaker, -createdAt, -row_id) %>% 
  rename(utterance=text) %>% 
  #filter(gameId=="3WzEi9zkHF77vdTw5") %>% 
  write_csv(here("data/study1/exchanges.csv"))

combined <- exchanges %>% 
    group_by(gameId, targetNum, repNum,trialNum,numPlayers,playerId, target, role, countCorrect) %>%
  summarize(utterance = paste0(utterance, collapse = ' ')) %>% 
  write_csv(here("data/study1/combined.csv"))
```

# Post-process for NLP

## Content analyses

Very rough -- haven't done spelling  correction or "stop words wrt tangram" filtering
Of words the speaker says in the last round, when were they said by the speaker in earlier rounds for the same tangram?

```{r}
d.numPlayer <- d.round_results %>% select(numPlayers, gameId)
matches <- read_csv(here("data/study1/content/word_matches.csv")) %>% left_join(d.numPlayer, by="gameId")



location_first_match <- matches %>% 
  filter(later_rep==5) %>% 
  group_by(earlier_rep,gameId,numPlayers) %>% 
  summarize(overlap=mean(match))

ggplot(location_first_match, aes(x=earlier_rep, y=overlap, color=as.factor(numPlayers)))+geom_jitter(alpha=.5,width=.2, height=0)+facet_wrap(~numPlayers)+
    stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width=.2), color="black")
```
Overlap is higher in 2 than more than two situations. There also appears to be a "same player" effect -- note the higher amount for rounds 1 and 3 relative to 2 and 4 for 2 player, and 1 relative to others in 4 player. 

Maybe can run a logistic model predicting if a final word occurred in earlier round as ~ round_num*numPlayer + same_speaker ? 

```{r}
matches %>% filter(match) %>% 
  filter(later_rep==5) %>% 
  mutate(target=str_extract(target,"[A-Z]")) %>% 
  group_by(target, gameId,numPlayers) %>% 
  summarize(early=min(earlier_rep)) %>% 
  group_by(target, numPlayers,early) %>% 
  tally() %>% 
  group_by(numPlayers) %>% 
  summarize(pct=n/sum(n),
            early=early) %>% 
  ggplot(aes(x=numPlayers, y=pct, fill=as.factor(early)))+geom_col(position="stack")
  
```
Want to look at how early these content words are introduced -- this is not the right graph for it, but there seems to be a lot more conventions staying from the first round in 2 player. Will need to check after doing elimination of non-content words. 