
\documentclass{stanfordletter}
%\makelabels
\begin{document}
	\name{Veronica Boyce}
	\signature{Veronica Boyce \\ Robert Hawkins \\ Noah D. Goodman \\ Michael C. Frank}
	
	
	\begin{letter}{Dr. Stavroula Kousta \\ Chief Editor \\ Nature Human Behavior}
		
		
          \opening{Dear Dr. Kousta,} 
          This
          submission contains the manuscript ``Interaction structure constrains the emergence of conventions in group communication''
          which we are submitting to Nature Human Behavior for
          publication. 
          
          How does communication work in large groups? While vast amounts of research addresses communication between dyads, methodological obstacles have mostly kept scientists from experimentally manipulating how larger groups build up common ground. 
          Our manuscript addresses this issue, reporting on a series of 3 experiments with 11 conditions and 1319 participants, where we examined the effects of varying group size and interaction structure on repeated reference games. We establish that the patterns of increasing accuracy and increasingly efficient utterances that are the hallmarks of two-player repeated reference games hold for 6-player groups even with limited communication channels. Critically, we found that smaller groups and groups with less-constrained interaction structures (“thick channels”) showed stronger convergence to group-specific conventions than large groups with constrained interaction structures (“thin
          channels”), which struggled with convention formation.
          
          We believe this paper will be of broad
          interest to cognitive scientists.
		 
          Researchers with relevant expertise and interest who
          therefore might be appropriate reviewers include Si On Yoon, Abdullah Almaatouq, and 
		 Riccardo Fusaroli. 
		 
          This manuscript is not under review at any other
          venue. Please let us know if you need any further
          information in connection with this submission. We look
          forward to hearing from you regarding the manuscript!
          \closing{Sincerely,}
		
	\end{letter}
	
\end{document}




